The relative roles of genetic, ecological and environmental factors in species radiations

### 2017-11-02 paper/draft.tex
lay out m&ms

\section{Material and Methods}

\section{Results}

>>>>

\section{Material and Methods}
We use an individual based metacommunity model written in julia \cite{JULIALANG}.
Each individual is characterized by a set of genetically controlled traits and is submitted to processes of
establishment, competition, growth, (density independent) mortality, reproduction and dispersal.
Each of which processes is affected by the individuals' characteristics.
The simulation arena consists of a larger landmass (the mainland) holding an initial pool of evolving populations and a smaller, initially unpopulated island some distance apart.
During the course of the simulation, individuals may disperse from the mainland to the island, thus colonizing it.

A detailed protocol can be found in the appendix (\cite{grimm2010odd}, XXX).

We record the complete state of our simulation world at the end of a simulation run and each time the arena changes (geomorphological dynamics).
We additionally record every individual that colonizes the island to track it in the phylogeny.

Using the thus simulated data, we calculate a phylogeny of the extant species, species numbers, etc. [WHAT ELSE?]
\section{Results}
